Submission_ResourceCount

### 2022-09-12 SIOP2023/Counts/Submission_ResourceCount.Rmd
late pushes

```{r analysis-preferences, echo=FALSE}

knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)

@@

temp <- read.csv("initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

@@

incomplete <- read.csv("inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

@@

source("recodescript.R", local = knitr::knit_global())

@@

cor(data22[405:407], use="all.obs")   ## something to be told with resources and challenges

@@

@@

```{r correlation_table}
r <- corx::corx(data22[,c(405:410)],                    
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  landscape = TRUE,
                  escape = FALSE)

@@

>>>>

```{r setup, echo=FALSE}

knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
#knitr::opts_knit$set(root.dir=normalizePath('../'))
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

temp <- read.csv("..//JDRJournalSubmission//initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

@@

incomplete <- read.csv("..//JDRJournalSubmission//inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

@@

source("..//JDRJournalSubmission//recodescript.R", local = knitr::knit_global())

@@

@@

cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges

@@

```{r matching}

## Trying to figure out which characteristics have agreement

## 145 & 248 (attention checks)

data22$rh1  <- data22$item118 + data22$item203
data22$rh2  <- data22$item119 + data22$item204
data22$rh3  <- data22$item120 + data22$item205
data22$rh4  <- data22$item121 + data22$item206
data22$rh5  <- data22$item122 + data22$item207
data22$rh6  <- data22$item123 + data22$item208
data22$rh7  <- data22$item124 + data22$item209
data22$rh8  <- data22$item125 + data22$item210
data22$rh9  <- data22$item126 + data22$item211
data22$rh10 <- data22$item127 + data22$item212

```{r correlation_table, eval=FALSE}

r <- corx::corx(data22[,c(405:410)],                    
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  escape = FALSE)

@@

```{r regressions}

eng <- lm(engagement ~ hindrance + challenge + resource, data22)
bur <- lm(burnout ~ hindrance + challenge + resource, data22)
str <- lm(stress ~ hindrance + challenge + resource, data22)

summary(eng)
summary(bur)
summary(str)
```
